Phylogenetic adaptions to urban living in Australian birds

### 2018-04-07 ms.Rmd
methods getting pretty close... and results started a little bit.

## Response variable - an urbanization index
We used VIIRS night-time lights [@elvidge2017viirs] as a proxy of a bird's association with urban habitat. The VIIRS night-time lights measures the electric lighting present on Earth's surface which is generally associated with human settlement. There are also a significant number of steps (e.g., filtering out background noise, degraded data, and other light source contamination) which are used to ensure the validity of the data and its association with human settlement [@elvidge2017viirs]. For the 637,482 checklists which met our criteria above, we used the checklists' associated spatial coordinates and Google Earth Engine [@gorelick2017google] to assign the average radiance value calculated from the VIIRS layer. For each location, the average radiance was calculated within a 5 km buffer, in order to match the spatial scale of the checklists included and to minimize any potential bias in eBird sampling protocols.

@@

## Models

@@

## Urbanization index

### Phylogenetic signal
There was a distinct phylogenetic signal in our urbanization index measure (Fig. 2; XXXXX SIGNIFICANCE TEST).

>>>>

## Response variable - an urbanization index
We used VIIRS night-time lights [@elvidge2017viirs] as a proxy of a bird's association with urban habitat. The VIIRS night-time lights measures the electric lighting present on Earth's surface which is generally associated with human settlement. There are also a significant number of steps (e.g., filtering out background noise, degraded data, and other light source contamination) which are used to ensure the validity of the data and its association with human settlement [@elvidge2017viirs]. For the 637,482 checklists which met our criteria above, we used the checklists' associated spatial coordinates and Google Earth Engine [@gorelick2017google] to assign the average radiance value calculated from the VIIRS layer. For each location, the average radiance was calculated within a 5 km buffer, in order to match the spatial scale of the checklists included and to minimize any potential bias in eBird sampling protocols. Any radiance values which were negative were forced to 0.00001 (sensu CITATION!!!).

@@

## Models
Before modelling, the explanatory variables (Appendix 1) were investigated for collinearity, and brain size and body size were highly correlated. Due to the affect that collinearity can have on modelling [@cade2015model], we were inclined to drop one of the two correlated explanatory variables. Given that others using a continuous response measure of urbanization have found brain size to have no evidence of species' response to urban environments [@evans2011makes], we eliminated this trait from consideration. In so doing, it also increased the number of species to be included in our models.

We had two linear modelling approaches; one with and one without phylogenetic constraints. Our urbanization index was log-transformed in order to meet model assumptions. The explanatory variables used in the models were those listed in Appendix 1, with the exception of brain size.

For both approaches, we employed a model-averaging technique [@grueber2011multimodel] in which we 'dredged' all possible subsets of the model [@barton2016mumin]. The global model was weighted by a measure of error associated with the response variable. This was assessed as the proportion of the number of total observations of a species divided by the number of unique localities a species was observed from. This helps to give more weight in the model-fitting procedure to those species that had more observations in more unique locations (i.e., an assessment of reliability of the observations). The global model fit was assessed by averaging the R2 values [@nakagawa2013general; @nakagawa2017coefficient] for each model in the top-selected model-set. Additionally, we calculated the relative contribution of each explanatory variable [sensu @evans2011make] by **XXXXXXXXXXXXXXXX**. The phylogenetically constrained model was fit using the 'phylolm' function from the phylolm package [@ho2014phylolm]. In order to assess the model fit and relative effect sizes of explanatory variables in the phylogenetically constrained models we **XXXXXXXXXXXX**.

All models and analyses were conducted in the R computing environment [@r2017coreteam] and relied heavily on the tidyverse environment [@wickham2017tidyverse].

@@

## Urbanization index
For the 450 species included in the models the mean +- SD urbanization index was 1.00 +- 1.81, with a range from 0.00135 (Black Noddy and Black-naped Tern) to 11.851 (Powerful Owl; Fig. 2).

### Phylogenetic signal
There was a distinct phylogenetic signal in our urbanization index measure (Fig. 3; XXXXX SIGNIFICANCE TEST).

**MAYBE DO SOME MEAN index by FAMILY PRESENTATIONS HERE**.
